Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-09 W13report.tex
Ha ha last commit  Really...
Had neglected to add Paul to author list.  Corrected here.
Full DM author list.

\author{Andrew Becker, Simon Krughoff, Andrew Connolly, Russell Owen\vspace{-2ex}}
\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
\date{\vspace{-2ex}\today}

@@

Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
\begin{equation}
n_{corrected}(>\nu) = n(> k\nu)
\label{correction}
\end{equation}  
For our data we scale {\it down} $\nu$ in the model by $k = 0.975, 0.985 $~and~$ 0.99$ for 
v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
efficiency. This will be the subject of the Summer 2013 work.

>>>>

\author{
Andrew Becker (UW), Simon Krughoff (UW), Andrew Connolly (UW), \\
Russell Owen (UW), Paul Price (Princeton), Robyn Allsman (LSSTC), \\
Yusra Al Sayyad (UW), Jacek Becla (SLAC), Steve Bickerton (Kavli IPMU),\\
Jim Bosch (Princeton), Scott Daniel (UW), Greg Daues (NCSA),\\
Gregory Dubois-Felsmann (SLAC), Mike Freemon (NCSA),\\
Perry Gee (UC Davis), Bill Glick (NCSA),Steve Groom (IPAC),\\
Joshua Hoblitt (NOAO), Mario Juric (LSSTC), Jeff Kantor (LSSTC),\\
Ron Lambert (NOAO), Dustin Lang (CMU), Kian-Tat Lim (SLAC),\\
Robert Lupton (Princeton), Bruce Mather (NCSA), Serge Monkewitz (IPAC),\\
Knut Olsen (NOAO), Steve Pietrowicz (NCSA), Ray Plante (NCSA),\\
Dick Shaw (NOAO), Douglas Smith (SLAC), Schuyler Van Dyk (IPAC), \\
and Daniel Wang (SLAC)\\ 
{\it for LSST Data Management}
\vspace{-2ex}}
\title{Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}}
\date{\today}

@@

Specifically, we define scaling factor $k$ to correct the counts at a given threshold:
\begin{equation}
n_{corrected}(>\nu) = n(> k\nu)
\label{correction}
\end{equation}  
For our data we scale {\it down} $\nu$ in the model by $k = 0.975, 0.985 $~and~$ 0.99$ for 
v6866601, v6866602, and v6866603 respectively.  The data plotted with these corrections are shown
in the bottom row of Figure\ref{fig-fp_v_thresh}.  These results suggest our variance estimates 
are too {\it high}, and we are therefore detecting too {\it few} false detections.  This does not agree 
entirely with the analysis of the empirical variance, Section~\ref{sec-varmis} and Table~\ref{tab-variance1}, 
which suggest that our variance planes {\it underestimate} the true variance.  However, this makes clear that 
while we are at the level of the theoretical floor in false detection rate, it is imperative to track the 
variance in our data to at the 1\% level or better to optimize both the false detection rate, and the true detection
efficiency. This will be a subject of the Summer 2013 work.
